A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
update on unused dataset

#### Read in necessary data and model ####
cleaned_president_polls <-read_csv(file = here("data/02-analysis_data/cleaned_president_polls.csv"), show_col_types = FALSE)
cleaned_data_survey <- read_csv(file = here("data/02-analysis_data/national_polling.csv"), show_col_types = FALSE)
state_polling_data <- read_csv(file = here("data/02-analysis_data/state_polling_data.csv"), show_col_types = FALSE)
state_analysis <- read_csv(file = here("data/02-analysis_data/state_analysis.csv"), show_col_types = FALSE)

>>>>

#### Read in necessary data and model ####
cleaned_president_polls <-read_csv(file = here("data/02-analysis_data/cleaned_president_polls.csv"), show_col_types = FALSE)
